The supernova-regulated ISM - III. Magnetic fields in the multi-phase gas

### 2015-03-22 paper.tex

FAG -- notes -- include Beck, Fletcher, Berkhuijsen observations of magnetic 
fields \citep{2013AN....334..548B, MNR18065} and observation/estimates of multiphase structure 
\citep{CS74,MO77}

@@

%focusing on the the B1$\Omega$s model of the ISM. This model features supernova(SN)-driven turbulence with gravity, differential rotation, SN explosions (SNe), radiative cooling, photoelectric heating and other transport processes, where the dynamo is in a kinematic statistically-steady state \citep{GSFSM13,GSSFM13}.\\
%end FAG
Twelve snapshots in the time range, $1.40\Gyr<t<1.67\Gyr$ are used. 
This time range corresponds to the steady-state phase of the system. 
In addition, there are two potential SN remnants, which provide isolated 
structures of hot gas. 
In addition, a snapshot at $t=1.4$ Gyr is also presented 
(Figure \ref{fig:fld_lines}) to illustrate the effect of the hot phase on 
the magnetic field.

>>>>

FAG -- notes -- include Beck, Fletcher, Berkhuijsen observations of magnetic 
fields \citep{BAH13, MNR18065} and observation/estimates of multiphase structure 
\citep{CS74,MO77}

@@

%focusing on the the B1$\Omega$s model of the ISM. This model features supernova(SN)-driven turbulence with gravity, differential rotation, SN explosions (SNe), radiative cooling, photoelectric heating and other transport processes, where the dynamo is in a kinematic statistically-steady state \citep{GSFSM13,GSSFM13}.\\
%end FAG
Twelve snapshots in the time range, $1.40\Gyr<t<1.67\Gyr$ are used. 
This time range corresponds to the steady-state phase of the system. 
%CCE edit--------------------------------------------------------------------
%In addition, there are two potential SN remnants, which provide isolated 
%structures of hot gas. 
In addition, a snapshot at $t=1.4$ Gyr is also presented 
(Figure \ref{fig:fld_lines}) to illustrate the effect of the hot phase on 
the magnetic field. This snapshot is chosen because it contains a hot gas structure resembling a superbubble, which has length scale $\mathcal O(10^2)$pc, in all physical dimensions. Further the ISM is well stratified in this snapshot; there are no chimney structures of hot gas propagating throughout the simulation domain. This illustrates the contrast in the characteristics of the mean magnetic field lines between the warm and the hot phases.   
%CCE edit--------------------------------------------------------------------
